### 2019-11-25 Mathematical Statistics/ms_ch_02.rmd
ms, ch3
ms, ch3

library(ggplot2, quietly = TRUE, warn.conflicts = FALSE)
library(ggrepel, quietly = TRUE, warn.conflicts = FALSE)
library(ggthemes, quietly = TRUE, warn.conflicts = FALSE)
library(knitr, quietly = TRUE, warn.conflicts = FALSE)
library(kableExtra, quietly = TRUE, warn.conflicts = FALSE)
library(Rblpapi, quietly = TRUE, warn.conflicts = FALSE)
library(scales, quietly = TRUE, warn.conflicts = FALSE)
library(pander, quietly = TRUE, warn.conflicts = FALSE)
library(dplyr, quietly = TRUE, warn.conflicts = FALSE)
library(formattable, quietly = TRUE, warn.conflicts = FALSE)
library(grid, quietly = TRUE, warn.conflicts = FALSE)
library(gridExtra, quietly = TRUE, warn.conflicts = FALSE)
library(png, quietly = TRUE, warn.conflicts = FALSE)
library(extrafont, quietly = TRUE, warn.conflicts = FALSE)
library(tinytex, quietly = TRUE, warn.conflicts = FALSE)
library(stringr, quietly = TRUE, warn.conflicts = FALSE)
library(lubridate, quietly = TRUE, warn.conflicts = FALSE)
library(reshape2, quietly = TRUE, warn.conflicts = FALSE)
library(ggrepel, quietly = TRUE, warn.conflicts = FALSE)
library(mnormt, quietly = TRUE, warn.conflicts = FALSE)
library(Ecdat, quietly = TRUE, warn.conflicts = FALSE)
library(MASS, quietly = TRUE, warn.conflicts = FALSE)
library(copula, quietly = TRUE, warn.conflicts = FALSE)
library(fGarch, quietly = TRUE, warn.conflicts = FALSE)
library(forecast, quietly = TRUE, warn.conflicts = FALSE)
library(tseries, quietly = TRUE, warn.conflicts = FALSE)
library(gmodels, quietly = TRUE, warn.conflicts = FALSE)
library(rugarch, quietly = TRUE, warn.conflicts = FALSE)

@@

Does there exist a __q__ such that $F(q) = 0.05$?

>>>>

library(ggplot2, quietly = TRUE, warn.conflicts = FALSE)
library(ggrepel, quietly = TRUE, warn.conflicts = FALSE)
library(ggthemes, quietly = TRUE, warn.conflicts = FALSE)
library(knitr, quietly = TRUE, warn.conflicts = FALSE)
library(kableExtra, quietly = TRUE, warn.conflicts = FALSE)
library(Rblpapi, quietly = TRUE, warn.conflicts = FALSE)
library(scales, quietly = TRUE, warn.conflicts = FALSE)
library(pander, quietly = TRUE, warn.conflicts = FALSE)
library(dplyr, quietly = TRUE, warn.conflicts = FALSE)
library(formattable, quietly = TRUE, warn.conflicts = FALSE)
library(grid, quietly = TRUE, warn.conflicts = FALSE)
library(gridExtra, quietly = TRUE, warn.conflicts = FALSE)
library(png, quietly = TRUE, warn.conflicts = FALSE)
library(extrafont, quietly = TRUE, warn.conflicts = FALSE)
library(tinytex, quietly = TRUE, warn.conflicts = FALSE)
library(stringr, quietly = TRUE, warn.conflicts = FALSE)
library(lubridate, quietly = TRUE, warn.conflicts = FALSE)
library(reshape2, quietly = TRUE, warn.conflicts = FALSE)
library(ggrepel, quietly = TRUE, warn.conflicts = FALSE)
library(mnormt, quietly = TRUE, warn.conflicts = FALSE)
library(Ecdat, quietly = TRUE, warn.conflicts = FALSE)
library(MASS, quietly = TRUE, warn.conflicts = FALSE)
library(copula, quietly = TRUE, warn.conflicts = FALSE)
library(fGarch, quietly = TRUE, warn.conflicts = FALSE)
library(forecast, quietly = TRUE, warn.conflicts = FALSE)
library(tseries, quietly = TRUE, warn.conflicts = FALSE)
library(gmodels, quietly = TRUE, warn.conflicts = FALSE)
library(rugarch, quietly = TRUE, warn.conflicts = FALSE)
library(EnvStats, quietly = TRUE, warn.conflicts = FALSE)

@@

+ Does there exist a __q__ such that $F(q) = 0.05$?

No, the discrete nature of this distribution doesn't have a value that falls in this interval.

### 2019-11-25 Mathematical Statistics/ms_ch_03.rmd
ms, ch3
ms, ch3

library(ggplot2, quietly = TRUE, warn.conflicts = FALSE)
library(ggrepel, quietly = TRUE, warn.conflicts = FALSE)
library(ggthemes, quietly = TRUE, warn.conflicts = FALSE)
library(knitr, quietly = TRUE, warn.conflicts = FALSE)
library(kableExtra, quietly = TRUE, warn.conflicts = FALSE)
library(Rblpapi, quietly = TRUE, warn.conflicts = FALSE)
library(scales, quietly = TRUE, warn.conflicts = FALSE)
library(pander, quietly = TRUE, warn.conflicts = FALSE)
library(dplyr, quietly = TRUE, warn.conflicts = FALSE)
library(formattable, quietly = TRUE, warn.conflicts = FALSE)
library(grid, quietly = TRUE, warn.conflicts = FALSE)
library(gridExtra, quietly = TRUE, warn.conflicts = FALSE)
library(png, quietly = TRUE, warn.conflicts = FALSE)
library(extrafont, quietly = TRUE, warn.conflicts = FALSE)
library(tinytex, quietly = TRUE, warn.conflicts = FALSE)
library(stringr, quietly = TRUE, warn.conflicts = FALSE)
library(lubridate, quietly = TRUE, warn.conflicts = FALSE)
library(reshape2, quietly = TRUE, warn.conflicts = FALSE)
library(ggrepel, quietly = TRUE, warn.conflicts = FALSE)
library(mnormt, quietly = TRUE, warn.conflicts = FALSE)
library(Ecdat, quietly = TRUE, warn.conflicts = FALSE)
library(MASS, quietly = TRUE, warn.conflicts = FALSE)
library(copula, quietly = TRUE, warn.conflicts = FALSE)
library(fGarch, quietly = TRUE, warn.conflicts = FALSE)
library(forecast, quietly = TRUE, warn.conflicts = FALSE)
library(tseries, quietly = TRUE, warn.conflicts = FALSE)
library(gmodels, quietly = TRUE, warn.conflicts = FALSE)
library(rugarch, quietly = TRUE, warn.conflicts = FALSE)
library(quantmod, quietly = TRUE, warn.conflicts = FALSE)

@@

```{r, echo = T}
```

@@

```{r, echo = T}
```
c.) What proportion of the differences are as large or larger than the observed differences in mean times?

```{r, echo = T}
```

@@

```{r, echo = T}
```

@@

>>>>

library(ggplot2, quietly = TRUE, warn.conflicts = FALSE)
library(ggrepel, quietly = TRUE, warn.conflicts = FALSE)
library(ggthemes, quietly = TRUE, warn.conflicts = FALSE)
library(knitr, quietly = TRUE, warn.conflicts = FALSE)
library(kableExtra, quietly = TRUE, warn.conflicts = FALSE)
library(Rblpapi, quietly = TRUE, warn.conflicts = FALSE)
library(scales, quietly = TRUE, warn.conflicts = FALSE)
library(pander, quietly = TRUE, warn.conflicts = FALSE)
library(dplyr, quietly = TRUE, warn.conflicts = FALSE)
library(formattable, quietly = TRUE, warn.conflicts = FALSE)
library(grid, quietly = TRUE, warn.conflicts = FALSE)
library(gridExtra, quietly = TRUE, warn.conflicts = FALSE)
library(png, quietly = TRUE, warn.conflicts = FALSE)
library(extrafont, quietly = TRUE, warn.conflicts = FALSE)
library(tinytex, quietly = TRUE, warn.conflicts = FALSE)
library(stringr, quietly = TRUE, warn.conflicts = FALSE)
library(lubridate, quietly = TRUE, warn.conflicts = FALSE)
library(reshape2, quietly = TRUE, warn.conflicts = FALSE)
library(ggrepel, quietly = TRUE, warn.conflicts = FALSE)
library(mnormt, quietly = TRUE, warn.conflicts = FALSE)
library(Ecdat, quietly = TRUE, warn.conflicts = FALSE)
library(MASS, quietly = TRUE, warn.conflicts = FALSE)
library(copula, quietly = TRUE, warn.conflicts = FALSE)
library(fGarch, quietly = TRUE, warn.conflicts = FALSE)
library(forecast, quietly = TRUE, warn.conflicts = FALSE)
library(tseries, quietly = TRUE, warn.conflicts = FALSE)
library(gmodels, quietly = TRUE, warn.conflicts = FALSE)
library(rugarch, quietly = TRUE, warn.conflicts = FALSE)
library(quantmod, quietly = TRUE, warn.conflicts = FALSE)
library(gtools, quietly = TRUE, warn.conflicts = FALSE)

@@

```{r, echo = T}

mice.t <- c(8, 10, 15)
mice.c <- c(5, 9)

observed <- mean(mice.t) - mean(mice.c)

observed
```

@@

```{r, echo = T}

mice <- c(mice.t, mice.c)

treatment <- combinations(n = 5, r = 3, mice, repeats.allowed = F)

control <- matrix(nrow = 10, ncol = 2)
for( i in 1:nrow(control))
{
  control[i,] <- mice[!mice %in% treatment[i,]]
}

perms <- data.table(cbind(treatment, control))

colnames(perms) <- c("D1", "D2", "D3", "C1", "C2")

perms$Xd <- (perms$D1 + perms$D2 + perms$D3) / 3
perms$Xc <- (perms$C1 + perms$C2) / 2
perms$Diff <- round(perms$Xd - perms$Xc, 2)

\newpage

```{r, echo = F}
pretty_kable(perms, "Mice Permutations")
```

c.) What proportion of the differences are as large or larger than the observed differences in mean times?

```{r, echo = T}

gte.observed <- perms[Diff >= observed]

pretty_kable(gte.observed, "Greater than or Equal to Observed")

p1c <- nrow(gte.observed) / nrow(perms)

__Proportion of differences greater than or equal to observed: `r p1c*100`%__

@@

```{r, echo = T}

gte.t <- perms[ Xd >= mean(mice.t),]
pretty_kable(gte.t, "Mean Treatment Greater than Observed")

p1d <- nrow(gte.t) / nrow(perms)

__Proportion of treatment groups greater than observed: `r p1d*100`%__

@@

Your statistics professor comes to class with a big urn that she claims contains 9,999 blue marbels and 1 red marble.

You draw our one marble at random and finds that it is red.

Would you be willing to tell your professor that you think she is wrong about the distribution of colors?

Why or why not?

What are you assuming in making your decision?

What if instead, she claims there are nine blue marbles and 1 red one (and you draw out a red marble)?

### 3.3

In a hypothesis test comparing two populations means, $H_0 : \mu_1 = \mu_2\ versus \ H_A : \mu_1 > \mu_2$

a.) Which P-value, 0.03 or 0.006 provides stronger evidence for the alternative hypothesis?

b.) Which P-value, 0.095 or 0.04 provides stronger evidence that chance alone might account for the observed result?

### 3.4

In the algorithms for conducting a permutation test, why do we add 1 to the number of replications N when calculating the P-Value?

### 3.5

In the flight delays case study in Section 1.1, the data contain flight delays for two airlines, American Airlines and United Airlines.

a.) Conduct a two-sided permutation test to see if the difference in mean delay times between the two carriers are statistically significant.

b.) The flights took place in May and June of 2009. Conduct a two-sided permutation test to see if the differences in mean delay times between two months is statistically significant.
